\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Steven Maharaj}
\title{Quant first project report}
\begin{document}
\maketitle

\section{The Quant workflow}
\begin{enumerate}
\item \textbf{Universe selection.} We define some universe of stocks that have some self similarity. Also, we should eliminate all stocks prohibited or illegal to trade.

\item \textbf{Single $\alpha$ factor model}. Define and evaluate individual expressions which rank the cross section of equities. 

\item \textbf{Alpha combination	}. Combine many single alpha factors into a signal $\alpha$ factor.  The combined alpha factor will have better prediction power than the best single alpha factor. This is because of the noise from the $\alpha$ factors cancel each other out.

\item \textbf{Risk model} Define and calculate a set of risk factors you want to use to constrain you portfolio.

\item \textbf{portfolio construction} Implement a process which takes your final combined alpha and your risk model and produces a target portfolio that minimises risk under your model.

\item \textbf{Execution Implement} a trading process to transition the current portfolio to the target portfolio.
\end{enumerate}
\section{The Competition requirements}
First, you need to use a cross-sectional, long-short equity strategy. Inaddtion you must also have
\begin{itemize}

    \item Positive returns.
    \item Leverage between 0.8x-1.1x.
    \item Low position concentration.
    \item Low beta-to-SPY.
   \item Mid-range turnover.
   \item Long and short positions.
    \item Trades liquid stocks.
    \item Low exposure to sector risk.
   \item Low exposure to style risk.
   \item Place orders with Optimize API.

\end{itemize}


\section{Next things to research}
\begin{itemize}
\item Factor analysis \url{ https://www.quantopian.com/lectures/factor-analysis-with-alphalens}
\item Morningstar funementals  - fuel and the transport industry \\ \url{ https://www.quantopian.com/docs/data-reference/morningstar_fundamentals}
\end{itemize}

\end{document}